Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-16 paper/tv.tex
m

- \code{e_1} started before time limit \code{d}, by applying rules \code{[to_2]}, \code{[to_3]} and \code{[to_1]}, 
it produces the concrete sequence [\anyevent{A}; \code{\varphi(e_1^\prime)}], and \anyevent{A} takes less than \codeme{d} time-units. \\
By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
\s{\env \wedge (t{\leq}d), \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}$. \\
Then \code{\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})} is 
the witness such that \code{d, \env, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
\models (\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}. 
\\
- \code{e_1} never started, by applying rules \code{[to_4]}, 
it produces the concrete sequence [\code{\varphi(e_2)}], and it takes more than \codeme{d} time-units. \\
By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
\s{\env \wedge (t{>}d), (\es_2 \mysharp t)}$. \\
Then \code{\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)} is 
the witness such that \code{d, \env, [\varphi(e_2)]  
\models (\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)}.

\item \textbf{Deadline:}  
\input{rules/op_ddl.tex}
When $\zeta = (\env,  \textbf{deadline}  [d]\ e) {\rightarrow^*} (\env^\prime, ()) $, 
by applying rules \code{[ddl_1]}, \code{[ddl_2]}, 
it produces the concrete sequence [\code{\varphi(e)}], and it takes less than \codeme{d} time-units. \\
By \code{[FV\text{-}Deadline]}, $\vdash  \s{\env, \epsilon} \ \textbf{deadline}[d]\ e 
\ \s{\env \wedge (t{<}d), \es(e)\mysharp t}$. \\
Then \code{\env \wedge (t{<}d) \wedge \es(e)\mysharp t} is the witness such that 
\code{d, \env, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\

>>>>

- \code{e_1} started before time limit \code{d}, by applying rules \code{[to_2]}, \code{[to_3]} and \code{[to_1]}, 
it produces the concrete sequence [\anyevent{A}; \code{\varphi(e_1^\prime)}], and \anyevent{A} takes less than \codeme{d} time-units. \\
By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
\s{\env \wedge (t{\leq}d), \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}$. \\
Then \code{\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})} is 
the witness such that \code{d, \env^\prime, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
\models (\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}. 
\\
- \code{e_1} never started, by applying rules \code{[to_4]}, 
it produces the concrete sequence [\code{\varphi(e_2)}], and it takes more than \codeme{d} time-units. \\
By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
\s{\env \wedge (t{>}d), (\es_2 \mysharp t)}$. \\
Then \code{\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)} is 
the witness such that \code{d, \env^\prime, [\varphi(e_2)]  
\models (\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)}.

\item \textbf{Deadline:}  
\input{rules/op_ddl.tex}
When $\zeta = (\env,  \textbf{deadline}  [d]\ e) {\rightarrow^*} (\env^\prime, ()) $, 
by applying rules \code{[ddl_1]}, \code{[ddl_2]}, 
it produces the concrete sequence [\code{\varphi(e)}], and it takes less than \codeme{d} time-units. \\
By \code{[FV\text{-}Deadline]}, $\vdash  \s{\env, \epsilon} \ \textbf{deadline}[d]\ e 
\ \s{\env \wedge (t{<}d), \es(e)\mysharp t}$. \\
Then \code{\env \wedge (t{<}d) \wedge \es(e)\mysharp t} is the witness such that 
\code{d, \env^\prime, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\
